---
title: "RC 03: Chapter 2.4 - 2.6"
tutorial:
  id: "RC_03"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn further data visualization graphics, including linegraphs, histograms, and faceting.
---


```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(nycflights13)
library(tutorialExtras)
library(gradethis)
library(tutorial.helpers)
library(ggcheck)

early_january_weather <- weather %>% 
  dplyr::filter(origin == "EWR" & month == 1 & day <= 15)

gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
options(
  tutorial.exercise.timelimit = 60
  #tutorial.storage = "local"
  ) 
```


```{r, context = "server"}
grade_server("grade")
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r Name}
question_text("Name:",
              answer_fn(function(value){
                              if(length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
              correct = "submitted",
              allow_retry = FALSE )
```

## Instructions

Complete this tutorial while reading Sections 2.4 - 2.6 of the [textbook](https://nustat.github.io/intro-stat-data-sci/02-visualization.html). Each question allows 3 'free' attempts. After the third attempt a 10% deduction occurs per attempt.

You can check your current grade and the number of attempts you are on in the "View grade" section. You can click this button as often and as many times as you would like as you progress through the tutorial. Before submitting, make sure your grade is as expected.

### Goals

- Learn how to use and interpret a linegraph
- Learn to use and interpret a histogram
- Choose an appropriate number of bins for a histogram
- Use faceting to view plots by a category

## 5NG#2: Linegraphs

Linegraphs show the relationship between two numerical variables when the variable on the x-axis, also called the explanatory variable, is of a sequential nature; in other words there is an inherent ordering to the variable.

###

Examples of sequential variables include hours, days, weeks, years, etc

### Exercise 1

At the top of any document or script the first thing we need to do is load the needed packages.

### 

Load the `ggplot2` package followed by the `nycflights13` package using the `library()` function.

```{r linegraphs-1, exercise = TRUE}

```

```{r linegraphs-1-hint-1, eval = FALSE}
library(...)
library(...)
```

```{r linegraphs-1-solution, exercise.reveal_solution = FALSE}
library(ggplot2)
library(nycflights13)
```

```{r linegraphs-1-check}
grade_this_code()
```

###

The `ggplot2` package is used for making data visualizations and the `nycflights13` package contains the `weather` dataset that we will use in this next example.

### Exercise 2

Let’s get a sense for the `weather` data frame. Run `glimpse(weather)` in the code chunk.


```{r linegraphs-2, exercise = TRUE}

```

```{r linegraphs-2-hint-1, eval = FALSE}
glimpse(...)
```

```{r linegraphs-2-solution, exercise.reveal_solution = FALSE}
glimpse(weather)
```

```{r linegraphs-2-check}
grade_this_code()
```

###

We observe that the data frame has 15 variables and 26,115 observations. There is a variable called `temp` of hourly temperature recordings in Fahrenheit at weather stations near all three airports in New York City.

### Exercise 3

For simplicity, we are going to work with a subset of this dataframe called `early_january_weather` which only includes hourly temperatures at the Newark airport for the first 15 days in January.

###

Click "Submit Answer" to create this new dataset.

```{r linegraphs-3, exercise = TRUE}
early_january_weather <- weather %>% 
  filter(origin == "EWR" & month == 1 & day <= 15)
```

```{r linegraphs-3-hint-1, eval = FALSE}
early_january_weather <- weather %>% 
  filter(origin == "EWR" & month == 1 & day <= 15)
```

```{r linegraphs-3-solution, exercise.reveal_solution = FALSE}
early_january_weather <- weather %>% 
  filter(origin == "EWR" & month == 1 & day <= 15)
```

```{r linegraphs-3-check}
grade_this_code()
```

###

We will learn more about data wrangling in Chapter 3. The `filter()` function subsets the data frame to only contain rows that meet the criteria specified. In this case the origin is "EWR" and the month is January and the day is less than or equal to 15.

### Exercise 4

Just like with a scatterplot, we will initialize the plot with the `ggplot()` function and set the first argument to be `data = early_january_weather`.

```{r linegraphs-4, exercise = TRUE}

```

```{r linegraphs-4-hint-1, eval = FALSE}
ggplot(data = ...)
```

```{r linegraphs-4-solution, exercise.reveal_solution = FALSE}
ggplot(data = early_january_weather)
```

```{r linegraphs-4-check}
grade_this_code()
```

### 

You should see a blank, grey square. R has set up the area in which it can place a plot.


### Exercise 5

Copy the previous code and specify the aesthetic mapping. 

Specifically:

- within `ggplot()` type `mapping = aes()`
- then map the variable `time_hour` to the `x` position aesthetic.
- and map the variable `temp` to the `y` position aesthetic 

```{r linegraphs-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r linegraphs-5-hint-1, eval = FALSE}
ggplot(data = early_january_weather, 
       mapping = aes(x = ..., y = ...))
```

```{r linegraphs-5-solution, exercise.reveal_solution = FALSE}
ggplot(data = early_january_weather, 
       mapping = aes(x = time_hour, y = temp))
```

```{r linegraphs-5-check}
grade_this_code()
```


### Exercise 6

Copy the previous code and use the `+` operator to add `geom_line()`.

```{r linegraphs-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r linegraphs-6-hint-1, eval = FALSE}
ggplot(data = early_january_weather, 
       mapping = aes(x = time_hour, y = temp)) + 
  geom_...
```

```{r linegraphs-6-solution, exercise.reveal_solution = FALSE}
ggplot(data = early_january_weather, 
       mapping = aes(x = time_hour, y = temp)) +
  geom_line()
```

```{r linegraphs-6-check}
grade_this_code()
```

###

Here, a linegraph is the most appropriate graphic because we are observing the relationship between two numeric variables AND `time_hour` has an inherent ordering, like some notion of time.

## 5NG#3: Histograms

If we are interested in the **distribution** of a single numeric variable one graph we can use is a histogram.

###

A distribution helps us understand:

 - What are the smallest and largest values?
 - What is the “center” value?
 - How do the values spread out?
 - What are frequent and infrequent values?


### Exercise 1

We will start by exploring the distribution of `temp`erature in the `weather` dataset.

###

Initialize the plot with the `ggplot()` function and set the first argument to be `data = weather`.

```{r histograms-1, exercise = TRUE}

```

```{r histograms-1-hint-1, eval = FALSE}
ggplot(data = ...)
```

```{r histograms-1-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather)
```

```{r histograms-1-check}
grade_this_code()
```

### 

You should see a blank, grey square. R has set up the area in which it can place a plot.


### Exercise 2

There will now be only one variable mapped in `aes(`): the single numerical variable `temp`. The y-aesthetic of a histogram gets computed for you automatically.

###

Within `ggplot()` set `mapping = aes(x = temp)`

```{r histograms-2, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r histograms-2-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = ...))
```

```{r histograms-2-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp))
```

```{r histograms-2-check}
grade_this_code()
```


### Exercise 3

Copy the previous code and use the `+` operator to add `geom_histogram()`.

```{r histograms-3, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r histograms-3-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) + 
  geom_...
```

```{r histograms-3-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) +
  geom_histogram()
```

```{r histograms-3-check}
grade_this_code()
```

###

A histogram divides the `x`-axis into **equally spaced bins**. 

The `y`-axis then tells us how many observations fall into the bin.

###

```{r histograms-3Q}
question_numeric("What is the default number of bins R uses to build a histogram?",
           answer(30, correct = TRUE),
           allow_retry = TRUE)
    
```


### Exercise 4

In the previous plot, it is difficult to see where one bin stops and another bin starts. Copy the previous code and add white borders around the bins by adding a `color = "white"` argument to `geom_histogram()`.

```{r histograms-4, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r histograms-4-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) + 
  geom_histogram(...)
```

```{r histograms-4-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) +
  geom_histogram(color = "white")
```

```{r histograms-4-check}
grade_this_code()
```

###

We can now better associate ranges of temperatures to each of the bins.

### Exercise 5

Copy the previous code and add `fill = "steelblue"` after the `color` argument within `geom_histogram()`.

```{r histograms-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r histograms-5-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) + 
  geom_histogram(color = "white", fill = ...)
```

```{r histograms-5-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) +
  geom_histogram(color = "white", fill = "steelblue")
```

```{r histograms-5-check}
grade_this_code()
```

###

There are 657 possible choices of color names that you could use.

###

In the **Console** of RStudio, type `colors()` and click enter.

```{r histograms-5Q}
question("What is the name of the last color from the output?",
           type = "learnr_text",
           answer_fn(function(value){
            if (str_remove_all(tolower(value), " ") %in%
                c("yellowgreen", "'yellowgreen'",
                  '"yellowgreen"')) {
                 return(mark_as(TRUE))}
                 return(mark_as(FALSE) )
                              }),
         allow_retry = TRUE
)
```


### Exercise 6

We saw previously that the default number of bins is 30. You will almost always need to test out a variety of different bin values or widths to find a value that is appropriate.

###

Copy the previous code and adjust the number of bins by setting the `bins` argument to `40`.

```{r histograms-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r histograms-6-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) + 
  geom_histogram(color = "white", fill = "steelblue",
                 bins = ...)
```

```{r histograms-6-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) +
  geom_histogram(color = "white", fill = "steelblue",
                 bins = 40)
```

```{r histograms-6-check}
grade_this_code()
```

### Exercise 7

Alternatively, instead of specifying the **number of bins** we can specify the **width of each bin**.

Copy the previous code remove `bins = 40`. This time add `binwidth = 10`.

```{r histograms-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r histograms-7-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) + 
  geom_histogram(color = "white", fill = "steelblue",
                 binwidth = ...)
```

```{r histograms-7-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = temp)) +
  geom_histogram(color = "white", fill = "steelblue",
                 binwidth = 10)
```

```{r histograms-7-check}
grade_this_code()
```

###

On the `x`-axis we can see that each bin now has a width of 10. For example, we can see one bin goes from 25 to 35 with nearly 3,000 observations in it.

###

It's important to note that you NEVER set BOTH `bin` and `binwidth`. You choose one or the other.

###

When choosing an appropriate `bin` size, it is important to balance the detail and readability of the histogram. Too few of bins hides the patterns and shape of the data. While too many bins adds noise and can make it difficult to interpret. 

You will likely test out **many** different `bin`s before picking the most appropriate one.


## Faceting

Faceting is used when we’d like to split a particular visualization of variables by another variable. This will create multiple copies of the same type of plot with matching x and y axes, but whose content will differ.

###

### Exercise 1

The code for a histogram of `temp`erature with a `binwidth` of 5 has been started for you.

Add on the layer `facet_wrap(~ month)` with the `+` operator.

```{r faceting-1, exercise = TRUE}
ggplot(data = weather, mapping = aes(x = temp)) +
  geom_histogram(binwidth = 5, color = "white")
```


```{r faceting-1-hint-1, eval = FALSE}
ggplot(data = weather, mapping = aes(x = temp)) +
  geom_histogram(binwidth = 5, color = "white") +
  ...
```

```{r faceting-1-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, mapping = aes(x = temp)) +
  geom_histogram(binwidth = 5, color = "white") +
  facet_wrap(~month)
```

```{r faceting-1-check}
grade_this_code()
```

###

The histogram is now split by the 12 possible months in a given year.

### Exercise 2

We can also specify the number of rows and columns in the grid by using the `nrow` and `ncol` arguments inside of `facet_wrap()`.

###

Copy the previous code and add the `nrow = 4` argument to `facet_wrap(~ month)`.

```{r faceting-2, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r faceting-2-hint-1, eval = FALSE}
ggplot(data = weather, mapping = aes(x = temp)) +
  geom_histogram(binwidth = 5, color = "white") +
  ...
```

```{r faceting-2-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, mapping = aes(x = temp)) +
  geom_histogram(binwidth = 5, color = "white") +
  facet_wrap(~month, nrow = 4)
```

```{r faceting-2-check}
grade_this_code()
```

<!-- ```{r} -->
<!-- question("Q4) Which of the following arguments in geom_histogram() will make the inside (as opposed to the outline) of the bars blue?", -->
<!--            answer(" bar = 'blue' "), -->
<!--            answer(" shade = 'blue' "), -->
<!--            answer(" color = 'blue' "), -->
<!--            answer(" fill = 'blue' ", correct = TRUE), -->
<!--            allow_retry = TRUE, -->
<!--            random_answer_order = TRUE) -->
<!-- ``` -->

<!-- ```{r} -->
<!--   question("Q1) What operator allows you to keep adding layers to a ggplot() object?", -->
<!--            type = "learnr_text", -->
<!--            answer_fn(function(value){ -->
<!--             if (str_remove_all(tolower(value), " ") %in% -->
<!--                 c("+", -->
<!--                   "plus", -->
<!--                   "plussign", -->
<!--                   "theplussign")) { -->
<!--                  return(mark_as(TRUE))} -->
<!--                  return(mark_as(FALSE) ) -->
<!--                               }), -->
<!--            allow_retry = TRUE) -->
<!--     question("Q2) Which of the following are typically used to visualize the relationship between two numeric variables? Select all that apply.", -->
<!--            answer("histogram"), -->
<!--            answer("boxplot"), -->
<!--            answer("scatterplot", correct = TRUE), -->
<!--            answer("linegraph", correct = TRUE), -->
<!--            allow_retry = TRUE, -->
<!--            random_answer_order = TRUE) -->

<!-- ``` -->


## View grade

```{r}
grade_button_ui(id = "grade")
```


## Submit

Once you are finished:

-   Click the 'Download Grade' button below. This will download an html document of your grade summary.
-   Make sure your grade is correct and as expected!
-   Submit the downloaded html to Canvas.

```{r}
grade_print_ui("grade")
```

