---
title: "Tutorial: Chapter 5.0 - 5.1"
tutorial:
  id: "isds_08"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn the basics of regression.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)

#for exercise
library(moderndive)
evals_ch5 <- evals %>%
  select(score, bty_avg, age)

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
options(tutorial.event_recorder = ISDStutorials::isds_recorder)
```


```{r, context = "server"}
rubric_list <- data.frame(question = c("Ex1", "Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8", "Q9", "Q10"),
                          points_possible = rep(1, 11))

grade_server("grade_out", 
            rubric_list = rubric_list)
```


```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
               style = "notes",
               correct = paste0(fontawesome::fa("check") ),
               incorrect = paste0(fontawesome::fa("xmark") ),
               allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block",
         grade_button_ui("grade_out") ),
     div(style="display:inline-block", print_ui("Print") )
)

# can have the grade output appear anywhere in your tutorial
grade_output_ui("grade_out")
```

## Instructions

Complete this tutorial while reading Sections 5.0 - 5.1 of the [textbook](https://nustat.github.io/intro-stat-data-sci/05-regression.html).

Once you are finished:

-   Click the 'grade tutorial' button at the top to retrieve your score.
-   Click the 'pdf' button to save the document as a pdf, you must have the tutorial open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


### Goals

-   Understand the essential components of basic regression.
-   Learn how to perform exploratory data analysis. 
-   Learn to perform simple linear regression.
-   Understand how to interpret fitted values and residuals.


## Exercise

Fill in the blanks of the code that creates a scatterplot of teaching score by beauty score and plots the regression line.

```{r Ex1, exercise=TRUE}
# Create the evals_ch5 dataset
evals_ch5 <- moderndive::evals %>%
  select(score, bty_avg, age)
# Create the scatterplot
ggplot(evals_ch5, aes(x = ___, y = ___)) +
   geom_point() +
   labs(___ = "Beauty Score",
        ___ = "Teaching Score",
        title = "Relationship of teaching and beauty scores") +
   geom____(method = ___)
```

```{r Ex1-hint-1}
Common language: y by x
```

```{r Ex1-solution, exercise.reveal_solution = FALSE}
# Create the evals_ch5 dataset
evals_ch5 <- moderndive::evals %>%
  select(score, bty_avg, age)
# Create the scatterplot
ggplot(evals_ch5, aes(x = bty_avg, y = score)) +
   geom_point() +
   labs(x = "Beauty Score",
        y = "Teaching Score",
        title = "Relationship of teaching and beauty scores") +
   geom_smooth(method = "lm")
```

```{r Ex1-code-check}
grade_this_code()
```


## Reading Quiz

```{r Q}

quiz(caption = NULL,
  # Q1
    question_wordbank("Q1) Match each of the following terms with whether they refer to the variable y or x in a data model.",
           choices = c("dependent variable", "outcomevariable", "predictor variable", "explanatory variable", "independent variable"),
           wordbank = c("x","y"),
           answer(c("y", "y", "x","x","x"), correct = TRUE),
           allow_retry = TRUE), 
    # Q2 
    question("Q2) What is the name of the commonly-used modeling technique that is the focus of Chapter 5? (Hint: it's two words)", 
           type = "learnr_text",
           answer_fn(function(value){
            if (tolower(value) %in% 
                c("linear regression")) {
                 return(mark_as(TRUE))}
                 return(mark_as(FALSE) ) }),
           allow_retry = TRUE),
     # Q3
    question("Q3) Which of the following are TRUE of a linear regression model? ",
           answer("an explanatory variable can be numerical or categorical", correct = TRUE),
           answer("it can include more than one explanatory variable, x", correct = TRUE),
           answer("an outcome variable can be numerical or categorical"),
           answer("it can include more than one outcome variable, y"),
           allow_retry = TRUE,
           random_answer_order = TRUE),  
    # Q4
    question("Q4) How many variables are in the data frame evals_ch5?", 
           type = "learnr_text",
           answer("3", correct = TRUE),
           allow_retry = TRUE),  
     # Q5
    question_wordbank("Q5) Match the following functions with their primary purpose.",
           choices = c("fit a linear regression model", "identify columns of a dataframe to keep", "identify rows of a dataframe to keep", "view summary information for each variable", "look at raw data"),
           wordbank = c("View()", "filter()", "lm()", "select()", "skim()"),
           answer(c("lm()", "select()", "filter()", "skim()", "View()"), correct = TRUE),
           allow_retry = TRUE),
    # Q6
    question("Q6) What is the maximum value of bty_avg  in the data frame evals? Round to two decimal places.", 
           type = "learnr_text",
           answer("8.17", correct = TRUE),
           allow_retry = TRUE),    
      # Q7
    question_wordbank("Q7) What is the primary purpose of the gapminder package?",
           choices = c("importing data files such as .csv", "data visualization", "includes datasets for analysis", "data wrangling", "computing summary statistics", "converting data to tidy format"),
           wordbank = c("readr", "ggplot2", "gapminder", "dplyr", "skimr", "tidyr"),
           answer(c("readr", "ggplot2", "gapminder", "dplyr", "skimr", "tidyr"), correct = TRUE),
           allow_retry = TRUE), 
    # Q8
    question("Q8) Which of the following can you conclude from the fact that the correlation coefficient between score and bty_avg is 0.187? Select all that apply.",
           answer("For every one unit increase in bty_avg , score increases by 0.187 on average."),
           answer("The slope of the best fit line for score vs. bty_avg is positive.", correct = TRUE),
           answer("As a bty_avg decreases, score also tends to decrease.", correct = TRUE),
           answer("There is a strong positive linear relationship between score and bty_avg."),
           allow_retry = TRUE,
           random_answer_order = TRUE),   
    # Q9
    question("Q9) Provide the slope of the regression line for score ~ bty_avg. Round to 3 decimal places.", 
           type = "learnr_text",
           answer("0.067", correct = TRUE),
           answer(".067", correct = TRUE),
           allow_retry = TRUE), 
    # Q10
    question("Q10) What is the fitted/predicted value for the 24th instructor in the evals_ch5 dataset when fitting the regression model score ~ bty_avg?", 
           type = "learnr_text",
           answer("4.25", correct = TRUE),
           allow_retry = TRUE)
)

```
