---
title: "Tutorial: Chapter 8"
tutorial:
  id: "isds_13"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn how to make inferences about the population from a sample.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
options(tutorial.event_recorder = ISDStutorials::isds_recorder)

```


```{r, context = "server"}
rubric_list <- data.frame(question = c("Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8"),
                          points_possible = rep(1, 8))

grade_server("grade_out", 
            rubric_list = rubric_list)
```


```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
               style = "notes_question",
               correct = paste0(fontawesome::fa("check") ),
               incorrect = paste0(fontawesome::fa("xmark") ),
               allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block",
         grade_button_ui("grade_out") ),
     div(style="display:inline-block", print_ui("Print") )
)

# can have the grade output appear anywhere in your tutorial
grade_output_ui("grade_out")
```

## Instructions

Complete this tutorial while reading Chapter 8 of the [textbook](https://nustat.github.io/intro-stat-ds/8-populations.html).

Once you are finished:

-   Click the 'grade tutorial' button at the top to retrieve your score.
-   Click the 'pdf' button to save the document as a pdf, you must have the tutorial open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


### Goals

-   Understand the difference between population parameters and sample estimators.
-   Be able to identify the different types of sampling.
-   Describe the difference between random sampling and random assignment, and know the appropriate conclusions that can be drawn from each.
-   Be able to determine the extent to which a study's results can be generalized.



## Reading Quiz

```{r Q}
quiz(caption = NULL,
  # Q1
    question_wordbank("Q1) Match each statistic with its corresponding population parameter.", 
           choices = c("\\(\\pi\\)", "\\(\\sigma\\)",
                       "\\(\\beta_1\\)", "\\(\\mu\\)", 
                        "\\(\\rho\\)", "\\(\\beta_0\\)"),
           wordbank = c("proportion", "standard deviation",
                        "regression slope", "mean",
                        "correlation", "regression intercept"),
           answer(c("proportion", "standard deviation",
                    "regression slope", "mean", 
                    "correlation", "regression intercept"), correct = TRUE),
           allow_retry = TRUE), 
    # Q2
  question_wordbank("Q2) Match each statistic with its corresponding sample estimator.", 
           choices = c("\\(r\\)", "\\(b_0\\)",
           "\\(\\hat{\\pi}\\)", "\\(\\bar{x}\\)",
           "\\(b_1\\)", "\\(s\\)"),
           wordbank = c("proportion", "standard deviation", "regression slope", "mean", "correlation", "regression intercept"),
           answer(c("correlation", "regression intercept",
                    "proportion", "mean", "regression slope",
                    "standard deviation"), correct = TRUE),
           allow_retry = TRUE), 
     # Q3
  question_wordbank("Q3) Match each of the following terms with whether they correspond to a sample or a population.", 
           choices = c("point estimate", "Roman letters", "census", "parameter", "hat notation", "Greek letters"),
           wordbank = c("sample", "population"),
           answer(c("sample", "sample", "population", "population", "sample", "population"), correct = TRUE),
           allow_retry = TRUE), 
          # Q4
  question_wordbank("Q4) Match each of the following steps in the sampling process with the appropriate order they should be conducted.", 
           choices = c("1st step", "2nd step", "3rd step", "4th step", "5th step"),
           wordbank = c("Define your population of interest", "Develop a population frame", "Develop a sampling plan", "Obtain your sample", "Collect data on your sample"),
           answer(c("Define your population of interest", "Develop a population frame", "Develop a sampling plan", "Obtain your sample", "Collect data on your sample"), correct = TRUE),
           allow_retry = TRUE), 
  #Q5
    question("Q5) Which of the following are TRUE about $\\bar{x}$? Select all that apply.",
           answer("It is an estimator for 
$\\sigma$"),
           answer("It is a measure of 'spread'"),
           answer("It is a point estimate", correct = TRUE),
           answer("It is a measure of 'center'", correct = TRUE),
           answer("It is a population parameter"),
           allow_retry = TRUE,
           random_answer_order = TRUE),  
    # Q6
 question_wordbank("Q6) Imagine you are conducting a survey among the Northwestern student body. You decide to sample 200 students. Match each of the following scenarios with the corresponding sampling procedures. ", 
           choices = c("50 students are randomly selected from each of the four classes (i.e. freshman, sophomores, juniors, seniors)", "200 students are randomly selected from a list of all NetIDs", "20 courses are randomly selected, and then 10 students are randomly selected from each course"),
           wordbank = c("stratified sampling", 
                        "simple random sampling", 
                        "cluster sampling"),
           answer(c("stratified sampling", 
                        "simple random sampling", 
                        "cluster sampling"), correct = TRUE),
           allow_retry = TRUE), 
    # Q7
    question("Q7) Which of the following statements are TRUE about random sampling? Select all that apply.",
           answer("Every unit in the population must have an equal probability of being selected"),
           answer("Every unit in the population must have a non-zero probability of being selected", correct = TRUE),
           answer("Individuals or units must be selected via a random process", correct = TRUE),
           answer("It enables us to generalize to the population we sampled from", correct = TRUE),
           answer("It requires a population frame to be developed or obtained in advance", correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE),   
    # Q8
question_wordbank("Q8) Match each of the following study types with the appropriate conclusions that can be drawn from them.", 
           choices = c("Random assignment", "Neither random sampling nor random assignment", "Random sampling", "Random sampling + random assignment"),
           wordbank = c("Causal claim within your sample only", 
                        "Associational claim within your sample only", "Associational claim, generalized to the whole population", "Causal claim, generalized to the whole population"),
           answer(c("Causal claim within your sample only", 
                        "Associational claim within your sample only", "Associational claim, generalized to the whole population", "Causal claim, generalized to the whole population"), correct = TRUE),
           allow_retry = TRUE)
)

```
