---
title: "Tutorial: Preface & Chapter 1"
tutorial:
  id: "isds_01"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn the basics of RMarkdown.
---

```{r setup, include=FALSE}

library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)

gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)

options(tutorial.event_recorder = ISDStutorials::isds_recorder)

```

```{r, context = "server"}
#must supply a data.frame consisting of "question" and "points_possible"
#The question/exercise name is the code chunk name followed by a number, ignoring all spaces and/or "-" symbols.
rubric_list <- data.frame(question = c("Ex1", "Ex1Q1", "Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8", "Q9", "Q10", "Q11"),
                          points_possible = rep(1, 13))

num_try = 3
deduction = 0.1
display = c("percent", "itemize") #options "itemize", "percent", "scaled"

grade_server("grade_out", 
            rubric_list = rubric_list, 
            num_try, deduction, display)
```

```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }), allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block",
         grade_button_ui("grade_out") ),
     div(style="display:inline-block", print_ui("Print") )
)

# can have the grade output appear anywhere in your tutorial
grade_output_ui("grade_out")
```

## Instructions

Complete this tutorial while reading the Preface and Chapter 1 of the [textbook](https://nustat.github.io/intro-stat-ds/).

Once you are finished:

-   Click the 'grade' button at the top to retrieve your score.
-   Click the 'pdf' button to save the document as a pdf, you must have the tutorial open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


### Goals

-   Know what resources you have available for help.
-   Understand the basics of R syntax and R output.
-   Understand the functions of important packages.
-   Understand how to find information from a dataframe.


## Exercises

Store the result of `20*40` into the variable `x`

```{r Ex1, exercise=TRUE}
x ___ 20*___
```

```{r Ex1-hint-1}
The assignment operator is `<-`
```

```{r Ex1-solution, exercise.reveal_solution = FALSE}
x <- 20*40
```

```{r Ex1-code-check}
grade_this_code()
```


```{r}

```


```{r Ex2-Q}
quiz(caption = NULL,
  question("Which of the following are names of variables in the flights data frame?",
           answer("air_time", correct = TRUE),
           answer("tailnum", correct = TRUE),
           answer("dplyr"),
           answer("Origin"),
           answer("dbl"),
           answer("glimpse"),
           answer("dep_delay", correct = TRUE),
           allow_retry = TRUE), 
  # Question 15
  question("What's the scheduled departure time for the first observation in the flights dataframe?",
           answer("600"),
           answer("515", correct = TRUE),
           answer("2013"),
           answer("830"),
           answer("517"),
           answer("554"), 
           allow_retry = TRUE) )
```


## Reading Quiz


```{r Q}
quiz(caption = NULL,
     question("What is a section of code in an RMarkdown document called?",
           answer("a tibble"),
           answer("a sandwich"),
           answer("a code letter",message = "Close, but not quite"),
           answer("a code chunk",correct = TRUE),
           allow_retry = TRUE),
  #Question 1
  question("What's the name of the online forum the authors mention with an extensive community of R users that you can consult for code troubleshooting?", 
           type = "learnr_text",
           answer("stackoverflow", correct = TRUE),
           answer("stackoverflow.com", correct = TRUE),
           allow_retry = TRUE),
  #Question 2
  question("Which of the following help ensure research is reproducible? Select all that apply.",
           answer("Copying and pasting results into a word processor"),
           answer("Using a workflow tool such as RMarkdown", correct = TRUE),
           answer("Literate programming (i.e. code that is readable)", correct = TRUE),
           answer("Well-documented data cleaning and analyses", correct = TRUE),
           allow_retry = TRUE), 
  # Question 3
  question("RStudio is:",
           answer("a programming language (like a car's engine)"),
           answer("an integrated development environment (like a car dashboard)", correct = TRUE),
           allow_retry = TRUE),
  # Question 4
  question("R is:",
           answer("a programming language (like a car's engine)", correct = TRUE),
           answer("an integrated development environment (like a car dashboard)"),
           allow_retry = TRUE),
  # Question 5
  question("Which of the following applications do you need to install on your computer for this course?",
           answer("R only"),
           answer("Both R and RStudio"),
           answer("RStudio only"),
           answer("None. RStudio Cloud uses your web browser.", correct = TRUE),
           allow_retry = TRUE),
  # Question 6
  question("Which of the following lines of code will store the value 30 in the object x? Select all that apply.",
           answer("x <- 15 + 15", correct = TRUE),
           answer("x = 30", correct = TRUE),
           answer("x <- 6*5", correct = TRUE),
           answer("x == 30"),
           allow_retry = TRUE), 
    # Question 7
    question_matching("Seeing red text in your console is not always bad. Order the three different types of feedback R gives (on right) to match how they should be interpreted.",
        choices = c("Error", "Warning", "Message"),
        answer(c("something is wrong! (red traffic light)","everything is working fine, but watch out/pay attention (yellow traffic light)", "everything is working fine (green traffic light)"), correct = TRUE), 
        allow_retry = TRUE ),
  # Question 10
  question("Which of the following is a good analogy for R packages?",
           answer("iOS software"),
           answer("iPhone accessories"),
           answer("apps you can download"),
           answer("a new iPhone", correct = TRUE),
           allow_retry = TRUE), 
  # Question 11
  question("What is the primary purpose of the moderndive package?",
           answer("data wrangling"),
           answer("accompanies this book", correct = TRUE),
           answer("data visualization"),
           allow_retry = TRUE), 
  # Question 12
  question("What is the primary purpose of the ggplot2 package?",
           answer("data wrangling"),
           answer("accompanies this book"),
           answer("data visualization", correct = TRUE),
           allow_retry = TRUE), 
  # Question 13
  question("What is the primary purpose of the dplyr package?",
           answer("data wrangling", correct = TRUE),
           answer("accompanies this book"),
           answer("data visualization"),
           allow_retry = TRUE) 
)
```


