---
title: "Tutorial: Chapter 11"
tutorial:
  id: "isds_18"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn how to calculate and interpret p-values.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
options(tutorial.event_recorder = ISDStutorials::isds_recorder)

```


```{r, context = "server"}
rubric_list <- data.frame(question = c("Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8", "Q9"),
                          points_possible = rep(1, 9))

grade_server("grade_out", 
            rubric_list = rubric_list)
```


```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }), 
          style = "notes",
          correct = paste0(fontawesome::fa("check") ),
          incorrect = paste0(fontawesome::fa("xmark") ),
          allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block",
         grade_button_ui("grade_out") ),
     div(style="display:inline-block", print_ui("Print") )
)

# can have the grade output appear anywhere in your tutorial
grade_output_ui("grade_out")
```

## Instructions

Complete this tutorial while reading Chapter 11 of the [textbook](https://nustat.github.io/intro-stat-data-sci/11-p-values.html).

Once you are finished:

-   Click the 'grade tutorial' button at the top to retrieve your score.
-   Click the 'pdf' button to save the document as a pdf, you must have the tutorial open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


### Goals

-   Be able to define a null hypothesis.
-   Calculate p-values from test statistics.
-   Understand how to interpret p-values.

## Reading Quiz

```{r Q}
quiz(
  caption = NULL,
  # Question 1
    question("Q1) P-values rely on a mathematical technique known as a stochastic proof by _______ .", 
           type = "learnr_text",
           answer("contradiction", correct = TRUE),
           allow_retry = TRUE), 
    #question 2
  question_multidrop("Q2) Imagine that you wish to determine whether a new drug lowers cholesterol in at-risk patients, so you conduct a randomized experiment. You wish to compare the average cholesterol among those who took the drug vs. those who took a placebo. Match each step with the appropriate order for conducting a stochastic proof by contradiction. ",
  choices = c("Determine the sampling distribution of \\( \\frac{\\bar{x}_T - \\bar{x}_C - 0}{SE(\\bar{x}_T - \\bar{x}_C)} \\) and compute its value in your sample",
              "Use your p-value to determine the probability that the null hypothesis is true",
              "Compute a p-value from the t-distribution",
              "Use your p-value to determine how likely your observed value is under the null hypothesis",
              "Assume \\(\\mu_T = \\mu_C \\) (i.e. assume \\(\\mu_T - \\mu_C = 0 \\) )",
              "Assume \\(\\mu_T < \\mu_C \\) (i.e. that those in the treatment group have lower cholesterol on average)"),
  box = 3,
  arrange = "ordered",
  answer(c("Step 2", "This is not a valid step in a stochastic proof by contradiction", "Step 3", "Step 4",  "Step 1","This is not a valid step in a stochastic proof by contradiction"), correct = TRUE),
  allow_retry = TRUE
  ),
    # Q3
    question("Q3) You conduct a randomized clinical trial where participants are randomly assigned to a diet and exercise regimen and you want to test whether they experience imprpoved sleep quality (measured on a continuous numeric scale) compared to the control group. What is the appropriate null hypothesis?
             Note this requires determining what the population parameter of interest is (e.g. $\\pi,\\mu,\\pi_1 - \\pi_2,\\mu_T - \\mu_C,\\beta_0,\\beta_1$ )", 
           answer("$\\beta_0 = 0$"),
           answer("$\\pi_1 - \\pi_2 = 0$"),
           answer("$\\pi = \\pi_{national}$"),
           answer("$\\mu_1 - \\mu_2 = 0$",correct=TRUE),
           answer("$\\mu = \\mu_{national}$"),
           answer("$\\beta_1 = 0$"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
  # Q4
    question("Q4) You use a survey of a random sample of NU students to test whether the percentage of students experiencing depression at Northwestern differs by minority status (coded as a binary categorical variable). What is the appropriate null hypothesis?
             Note this requires determining what the population parameter of interest is (e.g. $\\pi,\\mu,\\pi_1 - \\pi_2,\\mu_T - \\mu_C,\\beta_0,\\beta_1$ )", 
           answer("$\\beta_0 = 0$"),
           answer("$\\pi_1 - \\pi_2 = 0$",correct=TRUE),
           answer("$\\pi = \\pi_{national}$"),
           answer("$\\mu_1 - \\mu_2 = 0$"),
           answer("$\\mu = \\mu_{national}$"),
           answer("$\\beta_1 = 0$"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
  # Q5
    question("Q5) You use a survey of a random sample of NU students to test whether the percentage of students experiencing depression at Northwestern differs from the national norm. What is the appropriate null hypothesis?
             Note this requires determining what the population parameter of interest is (e.g. $\\pi,\\mu,\\pi_1 - \\pi_2,\\mu_T - \\mu_C,\\beta_0,\\beta_1$ )", 
           answer("$\\beta_0 = 0$"),
           answer("$\\pi_1 - \\pi_2 = 0$"),
           answer("$\\pi = \\pi_{national}$",correct=TRUE),
           answer("$\\mu_1 - \\mu_2 = 0$"),
           answer("$\\mu = \\mu_{national}$"),
           answer("$\\beta_1 = 0$"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
  # Q6
    question("Q6) You fit a regression model to determine if there is a relationship between housing prices (X) and a measure of school quality (Y) across zipcodes. What is the appropriate null hypothesis?
             Note this requires determining what the population parameter of interest is (e.g. $\\pi,\\mu,\\pi_1 - \\pi_2,\\mu_T - \\mu_C,\\beta_0,\\beta_1$ )", 
           answer("$\\beta_0 = 0$"),
           answer("$\\pi_1 - \\pi_2 = 0$"),
           answer("$\\pi = \\pi_{national}$"),
           answer("$\\mu_1 - \\mu_2 = 0$"),
           answer("$\\mu = \\mu_{national}$"),
           answer("$\\beta_1 = 0$",correct=TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE),
    # Q7
    question("Q7) Which of the following are valid examples of a null hypotheses? Select all that apply.", 
           answer("$\\mu = 19.5$",correct=TRUE),
           answer("$\\beta_1 = 0$",correct=TRUE),
           answer("$\\mu_1 - \\mu_2 = 0$",correct=TRUE),
           answer("$\\bar{x} = 19.5$"),
           answer("$\\hat{\\pi}_1 - \\hat{\\pi}_2 = 0$"),
           answer("$b_0 = 0$"),
           answer("$\\pi = 0.5$",correct=TRUE),
           answer("$\\pi_1 - \\pi_2 = 0$",correct=TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE),
    # Q8
    question("Q8) Which of the following are TRUE statements about p-values? Select all that apply.", 
           answer("A small p-value indicates data as extreme as what you observed is unlikely to occur if the null hypothesis is true", correct = TRUE),
           answer("A p-value is the probability that the observed statistic was produced by chance alone"),
           answer("A p-value is the probability of observing a t-statistic as extreme as the one you did assuming the null hypothesis is true", correct = TRUE),
           answer("A large p-value indicates you observed a large effect"),
           answer("A p-value is the probability that the null hypothesis is true"),
           answer("A p-value is the probability that the alternative hypothesis is true"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
      # Q9
    question("Q9) Assume for the context of your research question, you decide that a p-value < 0.1 is considered 'small.' Which of the following t-statistic values, if observed and calculated from your data, would result in 'small' p-values (i.e. p-value < 0.1)? Assume you have a sample of n = 1,000 people. Hint: You can use properties you know about the N(0,1) distribution since it is virtually equivalent to the t-distribution when the sample size is this large. Or you can use the function pt() to actually compute the p-values in R.", 
           answer("t-stat = -2.575", correct = TRUE),
           answer("t-stat = -1.7", correct = TRUE),
           answer("t-stat = -1"),
           answer("t-stat = 0.002"),
           answer("t-stat = 0.5"),
           answer("t-stat = 1.96", correct = TRUE),
           answer("t-stat = 3.2", correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE)
)

```
