---
title: "Tutorial: Chapter 3.4 - 3.9"
tutorial:
  id: "isds_06"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn how to perform more complex data wrangling.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)
library(nycflights13)

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
options(tutorial.event_recorder = ISDStutorials::isds_recorder)
```


```{r, context = "server"}
rubric_list <- data.frame(question = c("Ex1", "Ex1Q1", "Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7"),
                          points_possible = rep(1, 9))

grade_server("grade_out", 
            rubric_list = rubric_list)
```


```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
               style = "notes",
               correct = paste0(fontawesome::fa("check") ),
               incorrect = paste0(fontawesome::fa("xmark") ),
               allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block",
         grade_button_ui("grade_out") ),
     div(style="display:inline-block", print_ui("Print") )
)

# can have the grade output appear anywhere in your tutorial
grade_output_ui("grade_out")
```

## Instructions

Complete this tutorial while reading Sections 3.4 - 3.9 of the [textbook](https://nustat.github.io/intro-stat-data-sci/03-wrangling.html). Each question allows 3 'free' attempts. After the third attempt a 10% deduction occurs per attempt.

Once you are finished:

-   Click the 'grade tutorial' button at the top to retrieve your score.
-   Click the 'pdf' button to save the document as a pdf, you must have the tutorial open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


### Goals

-   Understand the functionality of `group_by`, `mutate`,`arrange`, and `join`.
-   Use these `dplyr` functions to perform data wrangling. 
-   Extract information from datasets using data wrangling.


## Exercise

Fill in the blanks for the code that merges the data frames `flights` and `airports` by their respective key variables "`dest`" and "`faa`". 


```{r Ex1, exercise=TRUE}
flights_with_airport_names <- ___  %>%
    inner____(airports, ___ = c("dest" = "faa"))
flights_with_airport_names
```


```{r Ex1-solution, exercise.reveal_solution = FALSE}
flights_with_airport_names <- flights  %>%
    inner_join(airports, by = c("dest" = "faa"))
flights_with_airport_names
```

```{r Ex1-code-check}
grade_this_code()
```

```{r Ex1-Q}
quiz(
  caption = "",
  question("Ex1 Q1) How many columns does the resulting dataset `flights_with_airport_names` have?",
           answer("9"),
           answer("1000"),
           answer("10"),
           answer("26",correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE)
)
```


## Reading Quiz

```{r Q}
quiz(
  caption = NULL,
  #Question 1
  question("Q1) How many flights departed from JFK in the flights dataset?", 
           type = "learnr_text",
           answer_fn(function(value){
                    if (value %in% c("111279", "111,279") ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
           allow_retry = TRUE),
  #Question 2
  question("Q2) Which function allows you to create a new variable?",
           answer("mutate()", correct = TRUE),
           answer("new_var()"),
           answer("create()"),
           answer("summarize()"),
           answer("group_by()"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
  #Question 3
  question("Q3) In the weather dataset, what is the average temperature in celcius in December?", 
           type = "learnr_text",
           answer("3.58", correct = TRUE),
           allow_retry = TRUE),
  # Q4
  question("Q4) What is the name of the dplyr function that allows you to sort the rows of a data frame by the alphanumeric order of a variable/column?", 
           type = "learnr_text",
           answer("arrange", correct = TRUE),
           answer("arrange()", correct = TRUE),
           allow_retry = TRUE),
  # Q5
    question_wordbank("Q5) Match the general description to the appropriate piece of code in the following code chunk: \n
      summary_temp <- weather %>% 
        summarize(mean = mean(temp), std_dev = sd(temp)) ",
        choices = c("name of the new summary data frame", 
                    "assignment operator",
                    "pipe operator",
                    "name of a new summary variable",
                    "name of data frame to be summarized"),
        wordbank = c("summary_temp", "<-", "%>%",
                 "std_dev", "weather"),
        answer(c("summary_temp", "<-", "%>%",
                 "std_dev", "weather"), correct = TRUE), 
        allow_retry = TRUE ),
  # Q6
  question("Q6) Which type of plot would be best to visualize differences in the distribution of life expectancy by continent?",
           answer("side-by-side boxplots", correct = TRUE),
           answer("scatterplot"),
           answer("barplot"),
           answer("histogram"),
           allow_retry = TRUE,
           random_answer_order = TRUE),
  #Q7
    question_wordbank("Q7) Match each dplyr verb with the task it accomplishes.",
            choices = c("only keep desired columns", 
                        "only keep rows that meet a criteria",
                        "create a new variable",
                        "compute the mean of a variable",
                        "sort by a variable"),
            wordbank = c("select()", "filter()", "mutate()",
                     "summarize()","arrange()"),
            answer(c("select()", "filter()", "mutate()",
                     "summarize()","arrange()"), 
                   correct = TRUE), 
            allow_retry = TRUE )
)

```
