---
title: "RC 06: Chapter 3.4 - 3.9"
tutorial:
  id: "RC_06"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn how to perform more complex data wrangling.
---


```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(tutorialExtras)
library(gradethis)
library(nycflights13)

gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
```


```{r, context = "server"}
grade_server("grade")
```

```{r Name}
question_text("Name:",
              answer_fn(function(value){
                              if(length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
              correct = "submitted",
              allow_retry = FALSE )
```

```{r}
grade_button_ui(id = "grade")
```

## Instructions

Complete this tutorial while reading Sections 3.4 - 3.9 of the [textbook](https://nustat.github.io/intro-stat-data-sci/03-wrangling.html). Each question allows 3 'free' attempts. After the third attempt a 10% deduction occurs per attempt.

You can click the "View Grade" button as many times as you would like to see your current grade and the number of attempts you are on. Before submitting make sure your grade is as expected.

### Goals

-   Extract information from datasets using data wrangling.
-   Understand the functionality of `group_by`, `mutate`,`arrange`, and a few other functions.
-   Use the pipe operator to link multiple operators at once.


## Exercises

**Exercise 1**

Fill in the blanks for the code to calculate the mean that standard deviation of the temperature **by** `month`. 

```{r Ex1, exercise=TRUE}
summary_monthly_temp <- weather %>% 
  ___(___) %>% 
  summarize(mean = mean(temp, na.rm = TRUE), 
            std_dev = sd(temp, na.rm = TRUE))

summary_monthly_temp
```


```{r Ex1-solution, exercise.reveal_solution = FALSE}
summary_monthly_temp <- weather %>% 
  group_by(month) %>% 
  summarize(mean = mean(temp, na.rm = TRUE), 
            std_dev = sd(temp, na.rm = TRUE))

summary_monthly_temp
```

```{r Ex1-code-check}
grade_this_code()
```

```{r Ex1-Q}
quiz(
  caption = "",
  question("Ex1 Q1) How many rows does the resulting dataset `summary_monthly_temp` have?",
           answer("1"),
           answer("12",correct = TRUE),
           answer("24"),
           answer("26,115"),
           allow_retry = TRUE,
           random_answer_order = TRUE)
)
```


**Exercise 2**

Fill in the blanks for the code to create a new variable that converts the temperature from Fahrenheit to Celsius in the `weather` dataset. This is calculated by using the existing variable `temp` subtracting 32 then dividing by 1.8. 

```{r Ex2, exercise=TRUE}
weather <- weather %>% 
  ___(temp_in_C = (___-32)/1.8)
```


```{r Ex2-solution, exercise.reveal_solution = FALSE}
weather <- weather %>% 
  mutate(temp_in_C = (temp-32)/1.8)
```

```{r Ex2-code-check}
grade_this_code()
```


## Reading Quiz

```{r Q}
quiz(
  caption = NULL,
  #Question 1
  question("Q1) How many flights departed from JFK in the flights dataset?", 
           type = "learnr_text",
           answer_fn(function(value){
                    if (value %in% c("111279", "111,279") ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
           allow_retry = TRUE),
  #Question 2
  question("Q2) In the weather dataset, what is the average temperature in celcius in December?", 
           type = "learnr_text",
           answer("3.58", correct = TRUE),
           allow_retry = TRUE),
  # Q4
  question("Q3) What is the name of the dplyr function that allows you to sort the rows of a data frame by the alphanumeric order of a variable/column?", 
           type = "learnr_text",
           answer("arrange", correct = TRUE),
           answer("arrange()", correct = TRUE),
           allow_retry = TRUE),
  # Q5
    question_wordbank("Q4) Match the general description to the appropriate piece of code in the following code chunk: \n
      summary_temp <- weather %>% 
        summarize(mean = mean(temp), std_dev = sd(temp)) ",
        choices = c("name of the new summary data frame", 
                    "assignment operator",
                    "pipe operator",
                    "name of a new summary variable",
                    "name of data frame to be summarized"),
        wordbank = c("summary_temp", "<-", "%>%",
                 "std_dev", "weather"),
        answer(c("summary_temp", "<-", "%>%",
                 "std_dev", "weather"), correct = TRUE), 
        allow_retry = TRUE ),
  # Q6
    question_wordbank("Q5) Match each dplyr verb with the task it accomplishes.",
            choices = c("only keep desired columns", 
                        "only keep rows that meet a criteria",
                        "create a new variable",
                        "compute the mean of a variable",
                        "sort by a variable"),
            wordbank = c("select()", "filter()", "mutate()",
                     "summarize()","arrange()"),
            answer(c("select()", "filter()", "mutate()",
                     "summarize()","arrange()"), 
                   correct = TRUE), 
            allow_retry = TRUE )
)

```

## Submit

Once you are finished:

-   Click the 'Download Grade' button below. This will download an html document of your grade summary.
-   Make sure your grade is correct and as expected!
-   Submit the downloaded html to Canvas.

```{r}
grade_print_ui("grade")
```

<br>
<hr /> 
<br>

<!-- ```{r} -->
<!-- bootstrapPage( -->
<!--      div(style="display:inline-block",  -->
<!--          strong("Optional:") ), -->
<!--      div(style="display:inline-block", -->
<!--          print_ui("Print", label = "full reading check") ), -->
<!--      div(style="display:inline-block",  -->
<!--          p("for your own review and records.") )  -->
<!--      ) -->
<!-- ``` -->
<!-- <hr />  -->
