---
title: "Tutorial: Chapter 5.2 - 5.4"
tutorial:
  id: "isds_09"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn how to perform more advanced linear regression.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
options(tutorial.event_recorder = ISDStutorials::isds_recorder)
```


```{r, context = "server"}
rubric_list <- data.frame(question = c("Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8", "Q9"),
                          points_possible = rep(1, 9))

grade_server("grade_out", 
            rubric_list = rubric_list)
```


```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
               style = "notes_question",
               allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block",
         grade_button_ui("grade_out") ),
     div(style="display:inline-block", print_ui("Print") )
)

# can have the grade output appear anywhere in your tutorial
grade_output_ui("grade_out")
```

## Instructions

Complete this tutorial while reading Sections 5.2 - 5.4 of the [textbook](https://nustat.github.io/intro-stat-ds/5-regression.html#model2).

Once you are finished:

-   Click the 'grade tutorial' button at the top to retrieve your score.
-   Click the 'pdf' button to save the document as a pdf, you must have the tutorial open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


### Goals

-   Learn how to perform regression for one categorical explanatory variable.
-   Understand the correlation coefficient.
-   Distinguish between correlation and causation.
-   Understand the line of best fit.


## Reading Quiz

```{r Q}
quiz(caption = NULL,
  # Question 1
    question("Q1) How many European countries are included in the gapminder 2007 dataset?", 
           type = "learnr_text",
           answer("30", correct = TRUE),
           allow_retry = TRUE),
    # Question 2
    question("Q2) What percent of countries in the gapminder2007 dataset have a life expectancy of less than 71.94?", 
           type = "learnr_text",
           answer("50", correct = TRUE),
           allow_retry = TRUE), 
      # Question 3
    question("Q3) How many years higher is the average life expectancy in Europe as compared to Africa? Round to 1 decimal place.", 
           type = "learnr_text",
           answer("22.8", correct = TRUE),
           allow_retry = TRUE),
       # Question 4
    question("Q4) What is the name of the explanatory variable in the lifeExp_model?", 
           type = "learnr_text",
           answer("continent", correct = TRUE),
           allow_retry = TRUE),
         # Question 5
    question("Q5) When x refers to the country Germany, what is the value of the indicator function $1_{Amer}(x)$?", 
           type = "learnr_text",
           answer("0", correct = TRUE),
           allow_retry = TRUE),
    # Question 6
    question("Q6) After fitting lifeExp_model to the gapminder2007 dataset, what is the value of $y - \\hat{y}$ for the country Angola? Round to 3 decimal places.", 
           type = "learnr_text",
           answer("-12.075", correct = TRUE),
           allow_retry = TRUE),
     # Question 7
    question("Q7) According to the lifeExp_model fit to the gapminder2007 dataset, what is the estimated life expectancy for the country Bangladesh? Round to 1 decimal place.", 
           type = "learnr_text",
           answer("70.7", correct = TRUE),
           allow_retry = TRUE),  
    # Question 8
    question("Q8) What is the potential confounding variable in the 'sleeping with shoes on' and 'waking up with a headache' example?", 
           type = "learnr_text",
           answer("alcohol", correct = TRUE),
           answer("drinking", correct = TRUE),
           answer("intoxicated", correct = TRUE),
           answer("intoxication", correct = TRUE),
           allow_retry = TRUE),  
     # Question 9
    question("Q9) If all the data points fall perfectly on the regression line, what would be the value of $\\sum_{i=1}^{n} (y_i - \\hat{y}_i)^2$?", 
           type = "learnr_text",
           answer("0", correct = TRUE),
           allow_retry = TRUE))


```
