---
title: "RC 04: Chapter 2.7 - 2.9"
tutorial:
  id: "RC_04"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn the final two of the 5NG: boxplots and barplots.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(nycflights13)
library(tutorialExtras)
library(gradethis)
library(tutorial.helpers)
library(ggcheck)

gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
options(
  tutorial.exercise.timelimit = 60
  #tutorial.storage = "local"
  ) 

fruits <- tibble(
  fruit = c("apple", "apple", "orange", "apple", "orange")
  )

fruits_counted <- tibble(
  fruit = c("apple", "orange"),
  number = c(3, 2)
  )
```


```{r, context = "server"}
grade_server("grade")
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r Name}
question_text("Name:",
              answer_fn(function(value){
                              if(length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
              correct = "submitted",
              allow_retry = FALSE )
```


## Instructions

Complete this tutorial while reading Sections 2.7 - 2.9 of the [textbook](https://nustat.github.io/intro-stat-data-sci/02-visualization.html). Each question allows 3 'free' attempts. After the third attempt a 10% deduction occurs per attempt.

You can check your current grade and the number of attempts you are on in the "View grade" section. You can click this button as often and as many times as you would like as you progress through the tutorial. Before submitting, make sure your grade is as expected.

### Goals

-   Learn to plot and interpret boxplots.
-   Learn to plot a single categorical variable.
-   Understand the different ways to visualize two categorical variables in a barplot.

## 5NG#4: Boxplots

Similar to a histogram, a boxplot shows the distribution of a single numeric variable. 

To compare distributions of a numerical variable split by another variable, another graphic besides a faceted histogram to achieve this is a side-by-side boxplot.

### Exercise 1

A boxplot is constructed from the information provided in the five-number summary of a numerical variable.

 
```{r boxplots-1}
question("Which of the following summary statistics are included in the five-number summary and are used to construct a boxplot when there are no “outliers” in the data?",
           answer("minimum", correct = TRUE),
           answer("maximum", correct = TRUE),
           answer("mode"),
           answer("first quantile (Q1, 25th percentile)", correct = TRUE),
           answer("standard deviation"),
           answer("third quantile (Q3, 75th percentile)", correct = TRUE),
           answer("median", correct = TRUE),
           answer("mean"),
           allow_retry = TRUE,
           random_answer_order = TRUE)
```

### Exercise 2

```{r boxplots-2}
question_wordbank("Drag and drop the features of a boxplot with the information they display about the data.",
        choices = c("lines extending from the box to points less than the 25th percentile or greater than the 75th percentile",
                 "interquartile range (i.e. a measure of the spread of the data)",
                 "outliers",
                 "1st quartile, median, 3rd quartile (i.e. the middle 50% of the data)"),
        wordbank = c("whiskers", "length", "dots", "box"),
        answer(c("whiskers", "length", "dots", "box"), 
        correct = TRUE), 
        allow_retry = TRUE )
```

### Exercise 3

Let’s create a side-by-side boxplot of hourly temperatures split by the 12 months as we did in the past tutorial with the faceted histograms.

###

Within `ggplot()` set the `data = weather`. Set the second argument to `mapping = aes()` and within `aes()` define:

- `x` to be the variable `month`
- `y` to be the numeric variable `temp`

```{r boxplots-3, exercise = TRUE}

```

```{r boxplots-3-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = ..., y = ...))
```

```{r boxplots-3-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = month, y = temp))
```

```{r boxplots-3-check}
grade_this_code()
```


### Exercise 4

Copy the previous code and use the `+` operator to add `geom_boxplot()`.

```{r boxplots-4, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r boxplots-4-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = month, y = temp)) +
  geom_...
```

```{r boxplots-4-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = month, y = temp)) +
  geom_boxplot()
```

```{r boxplots-4-check}
grade_this_code()
```

Oh no, this plot does not provide information about temperature separated by month! The warning messages clue us in as to why.

###
The first warning message is telling us that we have a “continuous”, or numerical variable, on the x-position aesthetic. Side-by-side boxplots require **one categorical** variable and one numeric variable.

### Exercise 5

Copy the previous code and convert the numerical variable month into a categorical variable by using the `factor()` function

```{r boxplots-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r boxplots-5-hint-1, eval = FALSE}
ggplot(data = weather, 
       mapping = aes(x = ...(month), y = temp)) +
  geom_boxplot()
```

```{r boxplots-5-solution, exercise.reveal_solution = FALSE}
ggplot(data = weather, 
       mapping = aes(x = factor(month), y = temp)) +
  geom_boxplot()
```

```{r boxplots-5-check}
grade_this_code()
```


## 5NG#5: Barplots

Another common task is visualize the distribution of a categorical variable. This is a simpler task, as we are simply counting different categories, also known as levels, of a categorical variable.

###

### Exercise 1

Below is the code we used to manually create two data frames, `fruit` and `fruit_counted`, representing a collection of fruit: 3 apples and 2 oranges.

```{r, echo = TRUE, eval = FALSE}
fruits <- tibble(
  fruit = c("apple", "apple", "orange", "apple", "orange")
  )

fruits_counted <- tibble(
  fruit = c("apple", "orange"),
  number = c(3, 2)
  )
```

###

Run `fruits` in the code chunk to print the data frame.

```{r barplots-1, exercise = TRUE}

```

```{r barplots-1-hint-1, eval = FALSE}
...
```

```{r barplots-1-solution, exercise.reveal_solution = FALSE}
fruits
```

```{r barplots-1-check}
grade_this_code()
```

###

Notice that `fruits` just lists the fruit individually.

### Exercise 2

Now, run `fruits_counted` in the code chunk to print the data frame.

```{r barplots-2, exercise = TRUE}

```

```{r barplots-2-hint-1, eval = FALSE}
...
```

```{r barplots-2-solution, exercise.reveal_solution = FALSE}
fruits_counted
```

```{r barplots-2-check}
grade_this_code()
```

###

`fruits_counted` has a variable `number` which represents pre-counted values of each fruit.

### Exercise 3

Let’s first generate a barplot using the `fruits` data frame where all 5 fruits are **listed individually** in 5 rows.

###

Use the `ggplot()` function with `data = fruits` and `mapping = aes(x = fruit)`.

Be careful the **data frame** is called `fruits` and the **variable** is called `fruit`.

```{r barplots-3, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r barplots-3-hint-1, eval = FALSE}
ggplot(data = ..., mapping = aes(x = ...))
```

```{r barplots-3-solution, exercise.reveal_solution = FALSE}
ggplot(data = fruits, mapping = aes(x = fruit))
```

```{r barplots-3-check}
grade_this_code()
```

### Exercise 4

Add a `geom_bar()` layer.

```{r barplots-4, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r barplots-4-hint-1, eval = FALSE}
ggplot(data = fruits, mapping = aes(x = fruit)) +
  geom_...
```

```{r barplots-4-solution, exercise.reveal_solution = FALSE}
ggplot(data = fruits, mapping = aes(x = fruit)) +
  geom_bar()
```

```{r barplots-4-check}
grade_this_code()
```

###

Since the data was in **list** form (not pre-counted), there is no `y`-aesthetic needed. 

### Exercise 5

Copy the previous code and make the following modifications:

- set `data = fruits_counted`
- add in `y = number` after the `x` aesthetic
- replace `geom_bar()` with `geom_col()`

```{r barplots-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r barplots-5-hint-1, eval = FALSE}
ggplot(data = fruits, mapping = aes(x = fruit)) +
  geom_...
```

```{r barplots-5-solution, exercise.reveal_solution = FALSE}
ggplot(data = fruits, mapping = aes(x = fruit, y = count)) +
  geom_col()
```

```{r barplots-5-check}
grade_this_code()
```

###

Since this data frame is pre-counted we need to specify the counts of each fruit as the `y` aesthetic (whereas `geom_bar()` counts the list for us). Recall from Exercise 2 the name of the variable was `number`.

###

```{r barplots-5Q}
question_wordbank("Which geometric layer do you use with categorical data that is...",
  choices = c("NOT pre-counted", "pre-counted"),
  answer(c("geom_bar()", "geom_col()"), correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE)
```

### Exercise 6

Recall our `flights` dataset from the `nycflights13` package. The package has already been pre-loaded for you and a `glimpse()` of the dataset is shown below.

```{r, echo = FALSE}
glimpse(flights)
```

###

Using `ggplot()` set the `data = flights` and assign the `x`-axis `aes`thetic to be `carrier`. Then add the appropriate `geom` layer.


```{r barplots-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r barplots-6-hint-1, eval = FALSE}
ggplot(data = ..., mapping = aes(x = ...)) +
  geom_...()
```

```{r barplots-6-solution, exercise.reveal_solution = FALSE}
ggplot(data = flights, mapping = aes(x = carrier)) +
  geom_bar()
```

```{r barplots-6-check}
grade_this_code()
```

###

Observe that United Air Lines (UA) had the most flights depart New York City in 2013 and SkyWest Airlines Inc. (OO) had the least.

###

If you don’t know which airlines correspond to which carrier codes, then run View(airlines) to see a directory of airlines.

### Exercise 7

Another use of barplots is to visualize the joint distribution of two categorical variables at the same time. 

###

Let’s examine the joint distribution of outgoing domestic flights from NYC by `carrier` and `origin`, or in other words the number of flights for each `carrier` and `origin` combination.

###

Copy the previous code and map the additional variable `origin` by adding a `fill = origin` inside the `aes()` aesthetic mapping

```{r barplots-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r barplots-7-hint-1, eval = FALSE}
ggplot(data = flights, mapping = aes(x = carrier, ...)) +
  geom_bar()
```

```{r barplots-7-solution, exercise.reveal_solution = FALSE}
ggplot(data = flights, mapping = aes(x = carrier, fill = origin)) +
  geom_bar()
```

```{r barplots-7-check}
grade_this_code()
```

###

This is an example of a **stacked barplot**. While easy to make it is not always the most ideal.


### Exercise 7

An alternative to stacked barplots are **side-by-side barplots**, also known as a **dodged barplot**. 

###

Copy the previous code and add the argument `position = "dodge"` within `geom_bar()`.

```{r barplots-8, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r barplots-8-hint-1, eval = FALSE}
ggplot(data = flights, mapping = aes(x = carrier, fill = origin)) +
  geom_bar(position = ...)
```

```{r barplots-8-solution, exercise.reveal_solution = FALSE}
ggplot(data = flights, mapping = aes(x = carrier, fill = origin)) +
  geom_bar(position = "dodge")
```

```{r barplots-8-check}
grade_this_code()
```

###

This shows the same information as a **faceted barplot**.


<!-- ## Reading Quiz -->

<!-- ```{r qz} -->
<!-- question("Q6) What is the preferred plot for visualizing a categorical variable?", -->
<!--            answer("barplot", correct = TRUE), -->
<!--            answer("pie chart"), -->
<!--            allow_retry = TRUE, -->
<!--            random_answer_order = TRUE) -->
<!-- ``` -->

<!-- ```{r Q} -->
<!-- quiz(caption = NULL, -->
<!--   question("Q3) Which of the following are visualization techniques that allow comparison of distributions of a numerical variable split or grouped by another variable? Select all that apply.", -->
<!--            answer("side-by-side boxplots", correct = TRUE), -->
<!--            answer("faceted histogram", correct = TRUE), -->
<!--            answer("scatterplot"), -->
<!--            answer("barplot"), -->
<!--            answer("linegraph"), -->
<!--            allow_retry = TRUE, -->
<!--            random_answer_order = TRUE), -->
<!--           # Q7 -->
<!--   question("Q7) Which of the following graphs can be used to visualize a single variable? Select all that apply.", -->
<!--            answer("linegraph"), -->
<!--            answer("barplot", correct = TRUE), -->
<!--            answer("boxplot", correct = TRUE), -->
<!--            answer("histogram", correct = TRUE), -->
<!--            answer("scatterplot"), -->
<!--            allow_retry = TRUE, -->
<!--            random_answer_order = TRUE),  -->
<!--   question("Q8) Which type of plot would be best to visualize differences in the distribution of life expectancy by continent?", -->
<!--            answer("side-by-side boxplots", correct = TRUE), -->
<!--            answer("scatterplot"), -->
<!--            answer("barplot"), -->
<!--            answer("histogram"), -->
<!--            allow_retry = TRUE, -->
<!--            random_answer_order = TRUE) -->

<!-- ) -->
<!-- ``` -->


## View grade

```{r}
grade_button_ui(id = "grade")
```


## Submit

Once you are finished:

-   Click the 'Download Grade' button below. This will download an html document of your grade summary.
-   Make sure your grade is correct and as expected!
-   Submit the downloaded html to Canvas.

```{r}
grade_print_ui("grade")
```

