---
title: "Tutorial: Chapter 2.7 - 2.9"
tutorial:
  id: "isds_04"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn the final two of the 5NG: boxplots and barplots.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(ISDStutorials)
library(gradethis)

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
options(tutorial.event_recorder = ISDStutorials::isds_recorder)
```


```{r, context = "server"}
rubric_list <- data.frame(question = c("Ex1", "Ex1Q1", "Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8"),
                          points_possible = rep(1, 10))

grade_server("grade_out", 
            rubric_list = rubric_list)
```


```{r isds-header}
# student name
question_blank("Name: ___",
                            answer_fn(function(value){
                              if (length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
               style = "notes_question",
               correct = paste0(fontawesome::fa("check") ),
               incorrect = paste0(fontawesome::fa("xmark") ),
               allow_retry = FALSE )
# have name, grade button, and print button on same line
bootstrapPage(
     div(style="display:inline-block",
         grade_button_ui("grade_out") ),
     div(style="display:inline-block", print_ui("Print") )
)

# can have the grade output appear anywhere in your tutorial
grade_output_ui("grade_out")
```

## Instructions

Complete this tutorial while reading Sections 2.7 - 2.9 of the [textbook](https://nustat.github.io/intro-stat-ds/2-viz.html#boxplots). Each question allows 3 'free' attempts. After the third attempt a 10% deduction occurs per attempt.

Once you are finished:

-   Click the 'grade tutorial' button at the top to retrieve your score.
-   Click the 'pdf' button to save the document as a pdf, you must have the tutorial open in a browser window for this button to work.
-   Submit the completed pdf to Canvas.


### Goals

-   Understand and interpret boxplots.
-   Learn to visualize different types of variables.

## Exercise

Construct a boxplot of `Species` by `Petal.Length` using the `iris` dataset by filling in the blanks (the data is already preloaded in R).

```{r Ex1, exercise=TRUE}
ggplot(data = ___, mapping = aes(x = ___, y = ___)) +
  ___()
```

```{r Ex1-hint-1}
Common language: y by x
```


```{r Ex1-solution, exercise.reveal_solution = FALSE}
ggplot(data = iris, mapping = aes(x = Petal.Length, y = Species)) +
  geom_boxplot()
```

```{r Ex1-code-check}
grade_this_code()
```

```{r Ex1-Q}
quiz(
  caption = "",
  question("Ex1 Q1) Which species' boxplot has no outliers?",
           answer("virginica",
                  correct = TRUE),
           answer("versicolor"),
           answer("setosa"),
           allow_retry = TRUE,
           random_answer_order = TRUE)
)
```


## Reading Quiz

```{r Q}
quiz(caption = NULL,
  # Q1
    question("Q1) Which of the following summary statistics are included in the five-number summary and are used to construct a boxplot when there are no “outliers” in the data?",
           answer("minimum", correct = TRUE),
           answer("maximum", correct = TRUE),
           answer("mode"),
           answer("first quantile (Q1, 25th percentile)", correct = TRUE),
           answer("standard deviation"),
           answer("third quantile (Q3, 75th percentile)", correct = TRUE),
           answer("median", correct = TRUE),
           answer("mean"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
  # Q2
    question_wordbank("Q2) Drag and drop the features of a boxplot with the information they display about the data.",
        choices = c("lines extending from the box to points less than the 25th percentile or greater than the 75th percentile",
                 "interquartile range (i.e. a measure of the spread of the data)",
                 "outliers",
                 "1st quartile, median, 3rd quartile (i.e. the middle 50% of the data)"),
        wordbank = c("whiskers", "length", "dots", "box"),
        answer(c("whiskers", "length", "dots", "box"), 
        correct = TRUE), 
        allow_retry = TRUE ),
        # Q3
  question("Q3) Which of the following are visualization techniques that allow comparison of distributions of a numerical variable split or grouped by another variable? Select all that apply.",
           answer("side-by-side boxplots", correct = TRUE),
           answer("faceted histogram", correct = TRUE),
           answer("scatterplot"),
           answer("barplot"),
           answer("linegraph"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
      # Q4
  question("Q4) Which geometric layer do you use with  categorical data that is NOT pre-counted?",
           answer("geom_bar()", correct = TRUE),
           answer("geom_col()"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
        # Q5
  question("Q5) Which geometric layer do you use with categorical data that is pre-counted?",
           answer("geom_bar()"),
           answer("geom_col()", correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
        # Q6
  question("Q6) What is the preferred plot for visualizing a categorical variable?",
           answer("barplot", correct = TRUE),
           answer("pie chart"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
          # Q7
  question("Q7) Which of the following graphs can be used to visualize a single variable? Select all that apply.",
           answer("linegraph"),
           answer("barplot", correct = TRUE),
           answer("boxplot", correct = TRUE),
           answer("histogram", correct = TRUE),
           answer("scatterplot"),
           allow_retry = TRUE,
           random_answer_order = TRUE), 
          # Q8
  question("Q8) Which of the following does ggplot() expect to be listed as the second argument by default?",
           answer("geom"),
           answer("mapping", correct = TRUE),
           answer("x"),
           answer("data"),
           allow_retry = TRUE,
           random_answer_order = TRUE)
)
```
