---
title: "RC 05: Chapter 3.0 - 3.3"
tutorial:
  id: "RC_05"
  version: 0.1
  
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Learn how to perform the basics of data wrangling.
---


```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(tutorialExtras)
library(gradethis)

gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
```


```{r, context = "server"}
grade_server("grade")
```

```{r Name}
question_text("Name:",
              answer_fn(function(value){
                              if(length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
              correct = "submitted",
              allow_retry = FALSE )
```

```{r}
grade_button_ui(id = "grade")
```

## Instructions

Complete this tutorial while reading Sections 3.0 - 3.3 of the [textbook](https://nustat.github.io/intro-stat-data-sci/03-wrangling.html). Each question allows 3 'free' attempts. After the third attempt a 10% deduction occurs per attempt.

You can click the "View Grade" button as many times as you would like to see your current grade and the number of attempts you are on. Before submitting make sure your grade is as expected.

### Goals

-   Understand and execute the basics of data wrangling.
-   Know how to use the pipe operator.
-   Use the `filter()` and `summarize()` functions.
-   Understand how to handle missing values.

## Exercise

Create a new data frame using the dataset `mpg` that is subsetted to include only cars from the year 1999 that get more than 30 miles per gallon on the highway by filling in the blanks (the data is already pre-loaded in R).

```{r Ex1, exercise=TRUE}
mpg_subset <- mpg ___
  filter(___ == "1999" & ___ >= 30)
```

```{r Ex1-hint-1}
Check out the data set `mpg` using ?mpg in the console (make sure you have the package ggplot2 loaded). 
```

```{r Ex1-solution, exercise.reveal_solution = FALSE}
mpg_subset <- mpg %>%
  filter(year == "1999" & hwy >= 30)
```

```{r Ex1-check}
grade_this_code()
```


## Reading Quiz

```{r Q}
quiz(
  caption = NULL,
  # Q1
  question("Q1) What is the name of the primary package we will use for data wrangling?", 
           type = "learnr_text",
           answer("dplyr", correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE),
  #Question 2
  question("Q2) What is the correct syntax for the 'pipe' operator?",
           answer("<-"),
           answer("->"),
           answer(" %>% ",correct=TRUE),
           answer(" %<% "),
           allow_retry = TRUE,
           random_answer_order = TRUE),
  #Question 3
  question("Q3) Which line of code will successfully create a new data frame flights_500mi containing only flights that travel at least 500 miles?",
           answer("flights_500mi <- flights %>% select(distance >= 500)"),
           answer("flights_500mi <- flights %>% select(distance > 500)"),
           answer("flights_500mi <- flight %>% mutate(distance > 500)"),
           answer("flights_500mi <- flights %>% mutate(distance >= 500)"),
           answer("flights_500mi <- flights %>% filter(distance >= 500)",correct=TRUE),
           answer("flights_500mi <- flights %>% filter(distance > 500)"),
           allow_retry = TRUE,
           random_answer_order = TRUE),
  #Question 4
  question("Q4) Which of the following is the correct syntax for 'not equal to'?",
           answer("NOT ="),
           answer("!=",correct=TRUE),
           answer("=!"),
           answer("=/"),
           answer("/="),
           allow_retry = TRUE,
           random_answer_order = TRUE),
  #Question 5
  question_numeric("Q5) What is the standard deviation of the variable temp in the weather dataset?",
           answer(17.8,correct=TRUE),
           #answer("17.8", correct = TRUE),
           step = 0.1,
           tolerance = 0.05,
           allow_retry = TRUE),
  #Question 6
  question("Q6) Which of the following arguments successfully removes missing values before computing a numerical summary (e.g. a mean, standard deviation, etc)?",
           answer("remove.missing = TRUE"),
           answer("NA.rm = TRUE"),
           answer("na.rm = TRUE",correct=TRUE),
           answer("remove.na = TRUE"),
           allow_retry = TRUE,
           random_answer_order = TRUE),
  #Question 7
  question("Q7) What is the default value for the na.rm argument in R?", 
           type = "learnr_text",
           answer("FALSE", correct = TRUE),
           answer("F", correct = TRUE),
           allow_retry = TRUE,
           random_answer_order = TRUE)
)

```

## Submit

Once you are finished:

-   Click the 'Download Grade' button below. This will download an html document of your grade summary.
-   Make sure your grade is correct and as expected!
-   Submit the downloaded html to Canvas.

```{r}
grade_print_ui("grade")
```
